---
title:"Shiny Application and Reproducible Pitch Project"
author: "suvi"
date: "May 13, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## *Itroduction*
 1.This project is part of developing data products course.
 2.The r presentation is generated using Rstudio.
 3.The Shiny application pitched by this presentation is at 
    http://127.0.0.1:5084/
 4. Code is available at https://github.com/sujv/Developing-Data-Product-course-project  



## *What is the purpose of the Shiny app?*

The cars dataset is used to predict the distance of the car from the speed of car.

## *How The Prediction Works:*
   Here we are predicting distance travelled by car from speed of the car .
   We are using *Linear regression* for the prediction.

```{r cars, echo=FALSE}
summary(cars)
model<-lm(dist~speed,data=cars)
pred<-predict(model,data=cars)
pred
```
## *Give It a Try:*
    The Shiny application pitched by this presentation is at 
    http://127.0.0.1:5084/
    Code is available at     https://github.com/sujv/Developing-Data-Product-course-project  
    











